NIRCam Calibration Plan

### 2016-12-03 ms.tex
I completed the NIRCam flux ladder w/ eposure times needed.

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& t$_{exp} (s) $\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	&  0.1 \\
2		& Bright JWST Calibrator			& G2 V			& 6	  		& On  &	32$\times$32	&   \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	&   \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	&   \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	&   \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	&   \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A.}
\vspace{0.05in}
\end{table}

@@

\begin{figure*}
\centering
\subfloat[Direct Imaging PSF]{
	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
	\label{fig:psfDirect}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
	\label{fig:psfND}
	}
	\caption{The direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop from \texttt{webbpsf}. Both images are normalized by the peak pixel value and have arbitrary array positions. Aperture photometry of the sources imaged through the corograph will have to use a large aperture encompassing the 6 outer peaks or apply careful background subtraction. Both PSFs were calculated for NIRCam's long wavelength channel with a F444W filter.}
	\label{fig:psfComparison}
\end{figure*}

>>>>

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter & t$_{exp} (s) $\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 \\
2		& Bright JWST Calibrator			& G2 V			& 6	  		& On &	64$\times$64	& F430M &  220 \\
3		& Bright JWST Calibrator			& G2 V			& 6  			& Off &	64$\times$64	& F430M &  0.1 \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A. The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.}
\vspace{0.05in}
\end{table}

@@

\begin{figure*}
\centering
\subfloat[Direct Imaging PSF]{
	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
	\label{fig:psfDirect}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
	\label{fig:psfND}
	}
	\caption{The direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop from \texttt{webbpsf}. Both images are normalized by the peak pixel value and have arbitrary array positions. Aperture photometry of the sources imaged through the corograph will have to use a large aperture encompassing the 6 outer peaks or apply careful background subtraction. Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.}
	\label{fig:psfComparison}
\end{figure*}
